Sparse Function-space Representation of Neural Networks

### 2023-05-30 workshop/main.tex
smalls

% if you use cleveref..
% \usepackage[capitalize,noabbrev]{cleveref}
%\usepackage[capitalize,nameinlink]{cleveref}
%\crefname{section}{Sec.}{Secs.}
%\crefname{appendix}{App.}{Apps.}
%\crefname{algorithm}{Alg.}{Algs.}

@@

% by linearising a neural network around the Maximum a Posteriori (MAP) weights.
% a GP posterior -- can be obtained
%
In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output), are usually trained to minimize the (regularized) empirical risk,\looseness-1
%
\begin{align} \label{eq-empirical-risk}
  \weights^{*} &= 
  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) \nonumber \\ &=
  \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
\end{align}
%
If $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
%Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
%The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ as it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
%Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
%However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
%In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset. 
The posterior over the weights ${p(\vw \mid \dataset) \propto p(y \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form. Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-purpose, but computationally heavy and impractical for downstream applications.

>>>>

% if you use cleveref..
% \usepackage[capitalize,noabbrev]{cleveref}
%\usepackage[capitalize,nameinlink]{cleveref}pdf
%\crefname{section}{Sec.}{Secs.}
%\crefname{appendix}{App.}{Apps.}
%\crefname{algorithm}{Alg.}{Algs.}

@@

% by linearising a neural network around the Maximum a Posteriori (MAP) weights.
% a GP posterior -- can be obtained
%
In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output), are usually trained to minimize the (regularized) empirical risk,\looseness-1
%
\begin{align} \label{eq-empirical-risk}
  \weights^{*} &= 
  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) \nonumber \\ &=
  \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
\end{align}
%
If $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
%Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
%The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ as it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
%Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
%However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
%In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset. 
The posterior over the weights ${p(\vw \mid \dataset) \propto p(y \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form. Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in ---are general-purpose, but computationally heavy and impractical for downstream applications.
